---
title: "writing functions"
author: "Purnima Sharma"
date: "11/8/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,          #aspect ratio: height over width
  out.width = "90%"      # figure doesn't go all the way out on full(100%) page
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", # to override ggplot default colors.
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do something simple (finding z-scores!)

```{r}
x_vec = rnorm(30, mean = 5, sd = 3) # create x-vector coming from normal distr, it has 30 numbers

(x_vec - mean(x_vec))/sd(x_vec)  #calculating z-scores of x-vector values
```

Using a function to compute z-scores instead.

```{r}
z_scores = function(x){     #creating function called z-scores, that has input x.
  
  z = (x - mean(x)) / sd(x)    # (body of the function) solve function using input x. Call the solved value z.
  
  return(z)
  
}

z_scores(x_vec)     #operate z-scores function on x-vector(created above:line31). So input is x_vec
```

Updating function so it works on valid inputs only.

```{r}
z_scores = function(x){
  
  if (!is.numeric(x)) {              # if x-input is not numeric, stop
    stop("input must be numeric")
  }
  
  if (length(x) < 3) {              # input should have alteast 3-values, if not, stop.
    stop("input must have atleast 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)    
  
  return(z)
  
}

z_scores(x_vec)    
```

## Trying a more complex function: Multiple outputs (want to calculate mean & sd too)

```{r}
mean_and_sd = function(x){
  
  if (!is.numeric(x)) {             
    stop("input must be numeric")
  }
  
  if (length(x) < 3) {             
    stop("input must have atleast 3 numbers")
  }
  
  mean_x = mean(x)     # find mean of x
  sd_x = sd(x)         # fidn sd of x   
  
  tibble(               # organize outputs in a table. Could have used "list" too.  
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Check that the function works.

```{r}
mean_and_sd(x_vec)    # use function mean_and_sd with input values of x-vector.
```

Checking with new x-vector

```{r}
x_vec = rnorm(1000)
mean_and_sd(x_vec) 
```

Multiple inputs (writing a function that will ask for sample size, mean and sd)
This is NOT a function! (function below, 2nd code)
```{r}
sim_data =  #create simulated dataset, that is a table, that has an x-column w/values:
  tibble(
    x = rnorm(n = 100, mean = 4, sd = 3)
  )

sim_data %>%   #summarize simulated dataset. Mean & sd should be close to above inputs!
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

This Is a function(same calculatons as above using a function):

```{r}
sim_mean_sd = function(sample_size, mu, sigma) {    #input these values,from row142
  
  sim_data =    
    tibble(
      x = rnorm(n = sample_size, mean = mu, sd = sigma) #inputs plugged here, as table
  )

  sim_data %>%   
    summarize(                            #table values used to find mean,sd of n=100 of normal distr, around given mean, sd          
      mean = mean(x),
      sd = sd(x)
)
  
}

sim_mean_sd(100, 4, 3)               # inputting values into function: row 127. Each time output will be diff, cause diff normal distr values will be generated.

#OR
sim_mean_sd(sample_size = 100, mu = 4, sigma = 3)  #name-matching input, vs position-matching (above row 142)  

```

Revisiting Napolean Dynamite ex (using functions)
Note a function (reading info from page 1 only):

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list.review-rating") %>%
  html_text() %>% 
  str_extract("^\\d") %>%   #get the first digit number at the beginning of that string
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Above code for page 1 only. To do multiple pages, use a function!
So, modifying above code and making it generic for any url.

```{r}

read_page_reviews = function(url){ #read_page_reviews is a function of url: i.e input is url 
  html = read_html(url)

  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list.review-rating") %>%
    html_text() %>% 
    str_extract("^\\d") %>%   #get the first digit number at the beginning of that string
    as.numeric()

  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = tibble(
    title = review_titles,
   # stars = review_stars,   *Not working for some reason:( running code without stars.
    text = review_text
    )
  
  reviews          # return object: will be a table of reviews
}
```

Trying above function on page 2 of "Dynamite" url.

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(dynamite_url)      #use function with this url
```

Reading a few pages of reviews of Napolean Dynamite!

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

# base is up to the number we are interested in.

dynamite_urls = str_c(dynamite_url_base, 1:5)    #base is pages 1 to 5, dynamite_urls will output urls of all 5 pages.

# reading all page reviews 1-5 and binding them together in a table

all_reviews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
  )
```

Functions as arguments.

```{r}
my_summary = function(x, sum_func) {
  
  sum_func(x)
  
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, mean)   # gives the same mean as above
my_summary(x_vec, median)  # same median as above
my_summary(x_vec, sd)
my_summary(x_vec, IQR)
```


